\LARGE \bf ***

### 2020-09-21 icra-2021.tex
some changes in the introduction (2)

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural applications such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy--with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying--along with strictly limited energy budgets. Currently, UAVs in precision agriculture use-cases are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

The energy is varied by means of mission-specific parameters, the Quality of Service (QoS) of the onboard computations, and the trajectory explicit equations (TEEs) parameters. The approach ideally accounts for a mission extension by adapting the QoS and TEEs as the UAV batteries drain. Preliminary data using a terrestrial fixed-wing UAV indicates a potential extension of up to 13 minutes over 1 hour by switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a path and a set of tasks the UAV is supposed to perform--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state observer--a Kalman filter--to cope with the uncertainty assumption. The algorithm selects the controls--the QoS and TEEs--dynamically using a modified tube-based output model predictive control (MPC), which ensures that state estimation error does not result in transgression of the control and state constraints.

Although underrepresented in precision agriculture and related literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied in the literature, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the--extensively studied--energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being--likewise the others--limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

@@

\begin{lem}\label{lem:state-vs-energy}
  Suppose the system behaves ideally (with no environment uncertainty and measurement error).
  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eq:state-details}) along their evolution~(\ref{eq:state-unct}) at time instant $k$ depends on the instantaneous energy consumption
  \begin{equation}
    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,0}\|\iff y_{k,0}\geq y_{k,1}.
  \end{equation}
\end{lem}
\begin{proof}
  *\\
\end{proof}

@@

\section{Algorithm}

>>>>

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies--often implemented utilizing unmanned aerial vehicles (UAVs)--are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy, with the UAV being, e.g., used to inform its grounded counterparts of obstacles detected while flying, along with strictly limited energy budgets. Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with such approaches as the energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the presented approach attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
Of particular inspiration to the approach is the technique of coupling the energy due to the computations performed and trajectory traveled, although being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

The algorithm adapts the energy dynamically, replanning mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. It ideally accounts for a mission extension by adapting both QoS and TEEs as the UAV flyes and its batteries drain. Firstly, the algorithm adapts QoS requiring the UAV to comprise robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters. Secondly, it adapts TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a time-varying path and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters boundaries--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption. The algorithm selects the controls (QoS and TEEs) dynamically using a modified tube-based output model predictive control (MPC), ensuring that state estimation error does not result in transgression of the control and state constraints.

The remainder of the paper is organized as follows. A suitable energy model for the path and the computations is showed in Section~\ref{sec:model}. The algorithm that uses the energy model to address dynamic mission planning is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

@@

\begin{lem}\label{lem:state-vs-energy}
  Suppose the system behaves ideally (with no environment uncertainty and measurement error).
  The magnitude of two arbitrary states $\mathbf{q}_{k,0},\mathbf{q}_{k,1}$ described in~(\ref{eq:state-details}) along their evolution~(\ref{eq:state-unct}) at time instant $k$ depends on the instantaneous energy consumption
  \begin{equation}
    \|\mathbf{q}_{k,0}\|\geq\|\mathbf{q}_{k,1}\|\iff y_{k,0}\geq y_{k,1}.
  \end{equation}
\end{lem}
\begin{proof}
  *\\
\end{proof}

@@

\section{Algorithm}
\label{sec:algo}
